---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# shinyecdm

<!-- badges: start -->
[![R build status](https://github.com/tmsalab/shinyecdm/workflows/R-CMD-check/badge.svg)](https://github.com/tmsalab/shinyecdm/actions)
[![Package-License](http://img.shields.io/badge/license-GPL%20(%3E=2)-brightgreen.svg?style=flat)](http://www.gnu.org/licenses/gpl-2.0.html)
<!-- badges: end -->

The goal of `shinyecdm` is to provide a user interface for the estimation routines
in the [`ecdm`](https://github.com/tmsalab/ecdm) R package.

## Installation

You can install `shinyecdm` from GitHub with:

```{r gh-installation, eval = FALSE}
if(!requireNamespace("remotes")) install.packages("remotes")
remotes::install_github("tmsalab/shinyecdm")
```

## Usage

Load the `shinyecdm` package into _R_: 

```r
library(shinyecdm)
```

Exploratory CDM models can be estimated with:

```r
shiny_edina()
```

## Details

The `shinyecdm` package is designed to provide a method for non-R aficionados 
to use the `ecdm` estimation routines. To do so, the `ecdm` routines are 
_wrapped_ into a web interface that is powered by the `shiny` package. As a 
result, the estimation methods can be served either _locally_ or _remotely_
through a server equipped with shiny.

## Authors

James Joseph Balamuta, Steven Andrew Culpepper, and Jeffrey Douglas

## Citing the shinyecdm package

To ensure future development of the package, please cite `shinyecdm`
package if used during an analysis or simulation studies. Citation information
for the package may be acquired by using in *R*:

```{r, eval = FALSE}
citation("shinyecdm")
```

## License

GPL (>= 2)
